\documentclass[11pt]{article}
\usepackage{resume}
\usepackage[rm]{roboto}
\def\name{Emily Crandall Fleischman}
\def\phone{(510) 520--2457}
\def\email{emilycf@mit.edu}
\def\termstreet{259 Saint Paul St.}
\def\termcity{Brookline, MA 02446}
\def\homestreet{3804 Everett Ave.}
\def\homecity{Oakland, CA 94602}

\begin{document}
\maketitle

\section{Education}
\def\employer{Massachusetts Institute of Technology}
\def\location{Cambridge, MA}
\def\title{Bachelor of Science in Civil Engineering}
\def\dates{2014--June 2019}
\begin{position}
\item Engineering coursework: Public Transportation Systems; Civil \& Environmental Engineering Design Lab; Programming for Engineering; Statistics for Engineering
\item Urban Planning coursework: Intro to Urban Design \& Development; Transportation Policy; Behavior \& Policy; Big Plans: Adapting to Climate Change; GIS Project Lab
\item Other relevant coursework: Microeconomics; Multivariate Calculus
\end{position}

\section{Relevant Experience}
\def\employer{Arup}
\def\location{New York, NY}
\def\title{Transportation Planning Intern}
\def\dates{June--August 2017}
\begin{position}
\item Researched alternative mobility options for suburban transportation networks.
\item Produced maps using ArcGIS and Adobe Illustrator for use in presentation to client.
\end{position}

\def\employer{San Francisco Bay Area Rapid Transit District (BART)}
\def\location{Oakland, CA}
\def\title{Intern}
\def\dates{July--August 2015}
\begin{position}
\item Developed use cases for IBM TRIRIGA TREES software.
\item Drafted change order for change in contract scope.
\end{position}

\def\employer{Market Street Railway}
\def\location{San Francisco, CA}
\def\title{Volunteer}
\def\dates{Summers 2012--2013}
\begin{position}
\item Catalogued and indexed documents relating to historical public transit in San Francisco, CA.
\end{position}

\section{Additional Experience}
\def\employer{Living Group Council (LGC)}
\def\location{Cambridge, MA}
\def\title{Speaker; Undergraduate Association Representative}
\def\dates{May 2015--February 2018}
\begin{position}
\item Organized and facilitated meetings of the LGC, the governing body of the five Independent Living Groups (ILGs) at MIT.
\item Represented the ILGs on committees, student government, and in meetings with administrators.
\item Spoke at events for new students and parents of new students.
\end{position}

\def\employer{Mobile Autonomous Systems Laboratory}
\def\location{Cambridge, MA}
\def\title{Participant/Programmer}
\def\dates{January 2015}
\begin{position}
\item Learned C++ in one month.
\item Programmed firmware for robot motors and infrared sensors using C++
\end{position}

\section{skills}
\begin{itemize}
\item Familiar with ArcGIS and QGIS software.
\item Proficient with MATLAB and NumPy.
\item Proficient with Microsoft Word, Excel, PowerPoint, and Access.
\item Self-taught programming in HTML, JavaScript, CSS, PHP, Python, Java, C, C++, Go, and Rust.
\item Proficient in Spanish, basic knowledge of French, Latin, and Old English.
\end{itemize}
\end{document}